Instability and inequality in the COVID-19 lockdown crime drop

### 2021-03-05 draft_paper.Rmd
heat maps tidy

That said, little is known about the localized drivers of these macro-level trends. An exploration of the extent to which the macro lockdown crime drop has been experienced equitably across space is valuable for two principal reasons. First, we would expect only a small number of fine-grained geographic units to have driven the lockdown crime drop. In pre-pandemic era, longitudinal studies have consistently demonstrated that, in a crime drop scenario, most local areas remained remarkably stable, with a disproportionatly large volume of change attributable to just handful of meso or micro-level units (e.g. @weisburd2004trajectories; @akmed2021mon; @curman2015crime; @bannister2018local). Findings have contributed to the evidence-base around routine activities theory, reflecing the considerable variation in criminal opportunities across (even spatially proximate) places [@eck2000finding; @weisburd2012criminology].

@@

>>>>

That said, little is known about the localized drivers of these macro-level trends. An exploration of the extent to which the macro lockdown crime drop has been experienced equitably across space is valuable for two principal reasons. First, we would expect only a small number of fine-grained geographic units to have driven the lockdown crime drop. In pre-pandemic era, longitudinal studies have consistently demonstrated that, in a crime drop scenario, most local areas remained remarkably stable, with a disproportionatly large volume of change attributable to just handful of meso or micro-level units (e.g. @weisburd2004trajectories; @akmed2021mon; @curman2015crime; @bannister2018local). Findings have contributed to the evidence-base around routine activities theory, reflecing the considerable variation and concentration in criminal opportunities across (even spatially proximate) places [@eck2000finding; @weisburd2012criminology].

@@

```{r heatmaps, fig.pos = 'H', message=F, comment=F, warning=F, fig.cap = "Comparing clusters between equivalent months in 2020 and 2019 according to (a) absolute difference in counts, (b) relative percentage difference in counts, (c) average difference in LSOA counts.", fig.align='center'}
knitr::include_graphics("visuals/heatmaps_gg.png")
```
